Second-Generation Web Interface to Correcting ASR output

### 2018-03-26 2018-ftc-vancouver/webapp.tex
citations

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr{\uu}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
\end{filecontents}

@@

The adoption of Web Audio API allowed for big improvements in comparison with
the original implementation described by Kr\r{u}za 2012~\cite{kruuza2012making}.
There are four major differences between using the HTML \texttt{<audio>} tag
and the Web Audio API.

@@

We use React as the view library and Redux for state management. The good thing
about Redux is that it makes it easy to keep minimal state as the single source
of truth and everything that can be computed is computed, while avoiding
needless calculations. This is of course nothing new -- basically it is what we
know from database design as the normal representation.~\cite{codd1970relational}
It is the first time this approach reached the web front-end in such degree of
popularity though.

@@

>>>>

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr{\uu}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}

\end{filecontents}

@@

The adoption of Web Audio API~\cite{adenot2013web} allowed for big improvements
in comparison with the original implementation described by Kr\r{u}za
2012~\cite{kruuza2012making}. There are four major differences between using the
HTML \texttt{<audio>} tag and the Web Audio API.

@@

We use React as the view library and Redux\cite{abramov2015redux} for state
management. The good thing about Redux is that it makes it easy to keep minimal
state as the single source of truth and everything that can be computed is
computed, while avoiding needless calculations. This is of course nothing new --
basically it is what we know from database design as the normal
representation.~\cite{codd1970relational} It is the first time this approach
reached the web front-end in such degree of popularity though.

@@

\bibliography{citace}
\bibliographystyle{splncs03}
